Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-24 paper.tex
Updated Experiments
Improved experiment description.

@@

\subsubsection{Experiment 1} The goal of our first OneMax experiment was to
make sure our Life-Cycle algorithm worked as expected, converging on the
solution. For this experiment, we intentionally used delays (on the tenth of a
second magnitude) to follow the Life-Cycle algorithm behavior on the console
output. For this experiment, we compared the DEAP algorithm versus the
Life-Cycle using ten processes (on containers) where we show the summarized
results in Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows
their Box and Whisker chart.

\subsubsection{Experiment 2} The goal of our second experiment was to confirm
the Life-Cycle algorithm continued working as expected, converging on the
solution. For this experiment, we reduced the time used on delays (now on the
thousands of a second magnitude) to follow the Life-Cycle algorithm behavior.
For this experiment, we only used tournament selection for the reproduction, on
the first configuration running the Life-Cycle on ten processes, versus the
second configuration where we reduced the processes to the minimum basic 5. We
show the summarized results in Table~\ref{tab.fun_ackley5}, and
Figure~\ref{fig.fun_ackley} shows their Box and Whisker chart.

\subsubsection{Experiment 3} The goal of our third experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we only used tournament selection for
the reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death process, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in
Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows their Box
and Whisker chart.

>>>>

            This experiment's goal was to follow and study the behavior of our
            proposed strategy, to repeat the results in the same order as
            expected, in a reduced number of both time and evaluations. We
            selected Rastrigin Classic Benchmark Function for Optimization for
            this experiment. Figure~\ref{fig.fun_rastrigin} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Table~\ref{tab.fun_rastrigin5} and
            Table~\ref{tab.fun_rastrigin10} (for five and ten dimensions,
            respectively).

@@
